---
title: ''
output:
  html_document:
    code_folding: show
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r}
library(tidyverse)
theme_set(theme_minimal())

halldorsson_child_counts <- read_rds("../data/halldorsson_child_counts.rds") |> as.data.frame()
halldorsson_child_fract <- read_rds("../data/halldorsson_child_fract.rds") |> as.data.frame()
```

# Can the normality assumption be met on the fathers' age?

## Visual
```{r}
p1 <- ggplot(halldorsson_child_counts, aes(x = age_father)) +
  geom_histogram(binwidth = 1, fill = "deepskyblue3", color = "black") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(title = "Distribution of Fathers' age", x = "Fathers' Age", y = "Count")


p2 <- ggplot(halldorsson_child_counts, aes(x = log10(age_father))) +
  geom_histogram(binwidth = .05, fill = "deepskyblue3", color = "black") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(title = "Distribution of Fathers' age", x = "Fathers' Age (log)", y = "Count")

ggsave("figure_05_age_distr.png", plot = p1, width = 8, height = 6, path = "./../Figures/")
ggsave("figure_06_age_log_distr.png", plot = p2, width = 8, height = 6, path = "./../Figures/")
```

Seems kind of bimodal, as well as right skewed

# Shapiro-Wilk test
```{r}
shapiro.test(halldorsson_child_counts$age_father)

shapiro.test(log10(halldorsson_child_counts$age_father))
```

p-value is significant, we have to reject the null hypothesis of normal distribution
W = 0.93 is relatively far from 1

# Linear regression on counts data
```{r}
linear_counts <- lm(age_father ~ C_G + C_T + CpG_TpG + T_C + T_G + C_A + T_A, data = halldorsson_child_counts)

summary(linear_counts)
hist(linear_counts$residuals)
shapiro.test(linear_counts$residuals)
```

# Linear regression on counts data (log transformed age)

Trying a model fit on the log response variable

```{r}
linear_counts_log10_age <- lm(log10(age_father) ~ C_G + C_T + CpG_TpG + T_C + T_G + C_A + T_A, data = halldorsson_child_counts)

summary(linear_counts_log10_age)
hist(linear_counts_log10_age$residuals)
shapiro.test(linear_counts_log10_age$residuals)
var(linear_counts_log10_age$residuals)
qqplot(y = linear_counts_log10_age$residuals, x = rnorm(1000,  sd = sqrt(0.009857264)),xlab = "normal", ylab="observed")
```


